\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-23 related-work.tex
Save

The closest work to ours might be \citet{boite2004proo}--they try to support \textit{extended} inductive type and related proof reuse in Coq. This biggest difference lies in our (incomplete) adaption of Family Polymorphism -- we support proof reuse and extension by inheritance, but also support implementation swapping using overriding, and we also argue that Family Polymorphism can provide a better and cleaner way of organizing mechanized metatheory development. The other difference lies in the handling of the extension of the inductive type. In our paradigm, the discussion of \textit{extensible} inductive type and partial recursor is unavoidable, which characterizes all possible extension of a given inductive type. In their work, without using Family to organized the code, the extended inductive type can be considered as a different inductive type than the original one, possibly leading to more expression problem~\cite{wadler-ep}.

>>>>

The closest work to ours might be \citet{boite2004proo}--they try to support \textit{extended} inductive type and related proof reuse in Coq. This biggest difference lies in our (incomplete) adaption of Family Polymorphism -- apart from supporting proof reuse and extension by inheritance, we also support implementation swapping using overriding, and we also argue that Family Polymorphism can provide a better and cleaner way of organizing mechanized metatheory development. The other difference lies in the handling of the extension of the inductive type. In our paradigm, the discussion of \textit{extensible} inductive type and \textit{partial recursor} is unavoidable, which characterizes all possible extension of a given inductive type. In their work, without using Family to organized the code, the extended inductive type can be considered as a different inductive type than the original one, possibly leading to more expression problem~\cite{wadler-ep}. 
% Another similar work is proof weaving \citep{mulhern2006proof} but I don't see a evaluation section in that paper

The other work
